Cloud Supercomputing

### 2019-03-14 writing/paper/paper.tex
Some small changes to paper.

\documentclass[runningheads]{llncs}
\title{Cloud Supercomputing}
\author{$\ldots$}
\institute{$\ldots$}
\usepackage[american]{babel}
\usepackage[autostyle, english = american]{csquotes}
\usepackage[%
  % backend=biber,
  % url=false,
  % style=alphabetic,
  % backref=true,
  % hyperref=true,
  % maxnames=4,
  % minnames=3,
  % maxbibnames=99,
  % firstinits,
  % uniquename=init
  ]{biblatex}
\DefineBibliographyStrings{english}{%
  backrefpage = {see p.},
  backrefpages = {see pp.}
}
\addbibresource{../bibliography.bib}

@@

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
\newcommand{\diffCoeff}{\varepsilon}
\newcommand{\hyperFluxDef}{
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
    \Qj \QZZ
  \end{pmatrix}
}
\newcommand{\viscFluxDef}{
  \begin{pmatrix}
    0\\
     \stressT (\Q, \gradQ)  \\
     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
     0\\
   \end{pmatrix}
}%
We solve the reactive compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
\begin{equation}
 \label{eq:equation-set} 
%  \begin{array}{l}
%  \text{mass cons.} \\
%  \text{momentum cons.} \\
%  \text{energy cons.} \\
%  \text{cont.\ gas} 
% \end{array}
% :
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE\\
    \QZ
    \end{pmatrix}}_{\Q}
  +
  \divergence{
  \underbrace{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}_{\flux(\Q, \gradQ)}}
 =
  \underbrace{
  \begin{pmatrix}
    \source[\Qrho\phantom{\Qrho}]\\
    \source[\Qj]\\
    \source[\QE]\\
    \source[\QZ]
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}
which describes the time evolution of variables $\Q$ with respect to a flux $\flux(\Q, \gradQ)$ and a source $\source(\Q)$.
The vector of conserved quantities is given by
\begin{equation}
  \label{eq:conserved-variables}
 \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
\end{equation}
where $\Qrho$ is the density, $\Qj$ is the two or three-dimensional momentum, $\QE$ is the energy density and $\QZ$ is the mass fraction of the chemical reactant.
The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
\begin{equation}
  \label{eq:eos}
  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ - gz \right).
\end{equation}
The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
We set $\QZZ$ and $q_0$ to zero for scenarios without a reactive component.
We model the diffusive effects of the flow by the standard stress tensor
\begin{equation}
  \label{eq:stress-tensor}
  \stressT(Q, \nabla Q) =
  \mu
  \left(
  \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
  \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
  \right),
\end{equation}
with viscosity $\mu$.

Many realistic, atmospheric flows can be described by a pertubation over a background state that is in hydrostatic equilibrium
\newcommand{\backgroundPressure}{\overline{\pressure}}
\newcommand{\backgroundRho}{\overline{\Qrho}}
\begin{equation}
  \label{eq:hydrostatic-balance}
  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z).
\end{equation}
The momentum equation is dominated by the background flow in this case.
This leads to numerical instabilities.
We avoid this by splitting the pressure $\pressure = \backgroundPressure + \pressure'$ and density $\Qrho = \backgroundRho + \Qrho'$
\begin{equation}
  \label{eq:momentum-equation-split}
  \pdv{\Qj}{t}+ \divergence{ \left(
    \Qv \otimes \Qj + \bm{I} \pressure'
    \right)
  } + \viscFlux_\Qj
  =
  -g \bm{k} \Qrho'.
\end{equation}
The right side of this equation is implemented as a source term.

@@

The rest of this paper is organized as follows:
\begin{itemize}
\item Efficient, explicit \aderdg{}-scheme with shared and distributed memory parallelization.
\item An \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
\item Evaluation with standard \textsc{cfd} scenarios, atmospheric and reactive flows.
\end{itemize}

@@

We use the \aderdg{}-scheme as proposed in xxx together with a Rusanov-style flux, which is adapted for \pde{}s with diffusive terms.

Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
The total variation (\textsc{tv}) of this function is defined by
\begin{equation}
  \label{eq:tv}
  \tv \left[ f(\bm{x}) \right] =
  \Vert
\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
\Vert_1
\end{equation}
for each cell.
The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
We compute this efficiently with Gaussian quadrature over the collocated quadrature points.
\newcommand{\mean}{\mu}%
\newcommand{\std}{\sigma}%
\newcommand{\variance}{\std^2}%
\newcommand{\Trefine}{T_\text{refine}}%
\newcommand{\Tdelete}{T_\text{delete}}%
How can we decide whether a cell is important or not?
To resolve this conundrum, we compute the mean and the population standard deviation of the total variation of all cells.
It is important to note that we use the method of Chan/LeVeque to compute the modes in a parallel and numerical stable manner.
A cell is then considered to contain significant information if its deviates from the mean more than a given threshold.
This criterion can be described formally by
\begin{equation}
  \label{eq:refinement-criterion}
  \operatorname{evaluate-refinement}(\Q, \mu, \sigma) =
  \begin{cases}
    \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma \\
    \text{delete} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma \\
    \text{keep} & \text{otherwise}.
    \end{cases}
\end{equation}
The parameters $\Trefine > \Tdelete$ can be chosen freely.
Chebyshev's inequality
\begin{equation}
  \label{eq:chebychev}
  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2},
\end{equation}
with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.
This inequality holds for arbitrary distributions under the weak assumption that their mean $\mu$ and standard deviation $\sigma$ are finite~\cite{wasserman2004all}.

We use a muscl-hancock based finite volume limiting as proposed in xxx.
Briefly, we first compute a candidate solution with our \aderdg{}-scheme and check whether it is valid.
A solution is considered to be invalid if it is a non-finite floating point number or if it is unphysical, i.e.\ if the pressure or density are not positive.
\todo{dmp?}
In case of an invalid solution, we recompute the timestep with a limited \muscl{} finite volume method.

@@

\todo{Constants of fluids?}
A simple scenario is the Taylor-Green vortex.
It has an analytical solution in the incompressible limit which is given by
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) \cos(y) \\
- \cos(x) \sin(y) 
    \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C.
  \end{split}
\end{align}
In this equation, $C = \nicefrac{100}{\gamma}$ is a constant that governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
We use a viscosity of $\mu = 0.1$ and Cauchy boundary conditions.

@@

As a final example of standard flow scenarios, we consider the lid-driven cavity flow which initial conditions are given by a fluid at rest, with $\Qrho = 0, \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.

We consider a domain of size $\SI{\pi}{m} \times \SI{\pi}{\m} \text{?}$ which is surrounded by no-slip walls.
The flow is driven entirely by the upper wall which has a velocity of $v_x = \SI{1}{\m/s}$.
\begin{equation}\label{eq:atmosphere-constants}
    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = 10000, \qquad g = 9.81,
\end{equation}
Our atmospheric flow scenarios are described in terms of the potential energy
\begin{equation}
  \potT = T \left( \frac{p_0}{p} \right)^{R/c_p},
\end{equation}
with the reference pressure $p_o = \SI{10e5}{\Pa}$.

We compute the initial background density and pressure by inserting the assumption of a constant background energy in \cref{eq:hydrostatic-balance}.
The background atmosphere is then perturbed.
\todo{What about our weird boundary condition for heat flux and energy?}
Let
\begin{equation}
  \label{eq:radius}
  r^2 = (x - x_0)^2 + (z - z_0)^2
\end{equation}
denote the difference between spatial positions $x,z$ and the center of a bubble $x_c, z_c$.
For our first scenario, the cosine bubble, we use a pertubation of the form
\begin{equation}
  \label{eq:cos-pertubation-alt}
  \pertubationPotT = 
    \nicefrac{A}{2} \left( 1 + \cos(\pi r) \right) \left[ r \leq a \right]
\end{equation}
\begin{align}
  \label{eq:cos-pertubation}
  \pertubationPotT &= \begin{cases}
    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a, \\
    0 & r > a,
    \end{cases}
\end{align}
where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
We use the constants
\begin{equation}\label{eq:cosine-bubble}
  A = 0.5 \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
\end{equation}
We use a constant viscosity of $\mu = 0.1$.
For our second scenario, the cold bubble on top of a warm bubble, we use the pertubation of the form
\begin{equation}
  \label{eq:bubbles-pertubation}
  \pertubationPotT =
  \begin{cases}
    A & r \leq a, \\
    A \exp \left( - \frac{(r-a)^2}{s^2} \right) & r > a,
    \end{cases}
\end{equation}
where $s$ is the decay rate and $r$  is the radius to the center~\pcref{eq:radius}.
We have two bubbles, with constants
\begin{equation}
  \label{eq:bubbles-values}
\begin{alignedat}{6}
  & \text{warm:} \qquad && A = 0.5, \quad&& a = \SI{150}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{500}{\m,} \quad&& z_c = \SI{300}{\m},\\
  & \text{cold:} \qquad && A = -0.15, \quad&& a = \SI{0}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{560}{\m}, \quad&& z_c = \SI{640}{\m}.
  \end{alignedat}
\end{equation}
Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.

@@

\section{Conclusion}
Insert conclusion here.

>>>>

\documentclass[runningheads]{llncs}
\title{Cloud Supercomputing}
\author{Authors}
\institute{Institute}
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage[american]{babel}
\usepackage[autostyle, english = american]{csquotes}
\usepackage[%
  % backend=biber,
  % url=false,
  % style=alphabetic,
  % backref=true,
  % hyperref=true,
  % maxnames=4,
  % minnames=3,
  % maxbibnames=99,
  % firstinits,
  % uniquename=init
  ]{biblatex}
\DefineBibliographyStrings{english}{%
  backrefpage = {see p.},
  backrefpages = {see pp.}
}
\addbibresource{../bibliography.bib}

@@

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
\newcommand{\diffCoeff}{\varepsilon}
\newcommand{\hyperFluxDef}{
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
    \Qj \QZZ
  \end{pmatrix}
}
\newcommand{\viscFluxDef}{
  \begin{pmatrix}
    0\\
     \stressT (\Q, \gradQ)  \\
     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
     0\\
   \end{pmatrix}
}%
We solve the reactive compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
\begin{equation}
 \label{eq:equation-set} 
%  \begin{array}{l}
%  \text{mass cons.} \\
%  \text{momentum cons.} \\
%  \text{energy cons.} \\
%  \text{cont.\ gas} 
% \end{array}
% :
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE\\
    \QZ
    \end{pmatrix}}_{\Q}
  +
  \divergence{
  \underbrace{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}_{\flux(\Q, \gradQ)}}
 =
  \underbrace{
  \begin{pmatrix}
    \source[\Qrho\phantom{\Qrho}]\\
    \source[\Qj]\\
    \source[\QE]\\
    \source[\QZ]
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}
with vector of conserved quantitites $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
The conserved quantities
\begin{equation}
  \label{eq:conserved-variables}
 \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
\end{equation}
are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$ and the mass fraction of the chemical reactant $\QZ$.
The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
\begin{equation}
  \label{eq:eos}
  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ - gz \right).
\end{equation}
and relates to the temperature $T$ by the thermal equation of state
\begin{equation}
  \label{eq:temperature}
  \pressure = \Qrho R T,
\end{equation}
where $R$ is the specific gas constant of a fluid.

The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
We set $\QZZ$ and $q_0$ to zero for scenarios without a reactive component.
We model the diffusive effects of the flow by the standard stress tensor
\begin{equation}
  \label{eq:stress-tensor}
  \stressT(Q, \nabla Q) =
  \mu
  \left(
  \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
  \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
  \right),
\end{equation}
with viscosity $\mu$.

Many realistic, atmospheric flows can be described by a pertubation over a background state that is in hydrostatic equilibrium
\newcommand{\backgroundPressure}{\overline{\pressure}}
\newcommand{\backgroundRho}{\overline{\Qrho}}
\begin{equation}
  \label{eq:hydrostatic-balance}
  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z),
\end{equation}
i.e.\ a state where the pressure differences are exactly balanced with the gravitational source term.
The momentum equation is dominated by the background flow in this case.
This leads to numerical instabilities.
To avoid this, we split the pressure $\pressure = \backgroundPressure + \pressure'$ and density $\Qrho = \backgroundRho + \Qrho'$, arriving at the modified equation
\begin{equation}
  \label{eq:momentum-equation-split}
  \pdv{\Qj}{t}+ \divergence{ \left(
    \Qv \otimes \Qj + \bm{I} \pressure'
    \right)
  } + \viscFlux_\Qj
  =
  -g \bm{k} \Qrho'.
\end{equation}

@@

In the rest of the paper, we make the following contributions:
\begin{itemize}
\item Efficient, explicit \aderdg{}-scheme with shared and distributed memory parallelization.
\item An \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
\item Evaluation with standard \textsc{cfd} scenarios, atmospheric and reactive flows.
\end{itemize}

@@

We use the \aderdg{}-scheme as proposed in \cite{dumbser2008unified} together with a Rusanov-style flux~\cite{gassner2008discontinuous,fambri2017space} that is adapted for \pde{}s with diffusive terms.

Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
The total variation (\textsc{tv}) of this function is defined by
\begin{equation}
  \label{eq:tv}
  \tv \left[ f(\bm{x}) \right] =
  \Vert
\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
\Vert_1
\end{equation}
for each cell.
The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
We compute the integral efficiently with Gaussian quadrature over the collocated quadrature points.
\newcommand{\mean}{\mu}%
\newcommand{\std}{\sigma}%
\newcommand{\variance}{\std^2}%
\newcommand{\Trefine}{T_\text{refine}}%
\newcommand{\Tdelete}{T_\text{delete}}%
How can we decide whether a cell is important or not?
To resolve this conundrum, we compute the mean and the population standard deviation of the total variation of all cells.
It is important to note that we use the method of~\cite{chan1982updating} to compute the modes in a parallel and numerical stable manner.
A cell is then considered to contain significant information if its deviates from the mean more than a given threshold.
This criterion can be described formally by
\begin{equation}
  \label{eq:refinement-criterion}
  \operatorname{evaluate-refinement}(\Q, \mu, \sigma) =
  \begin{cases}
    \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma \\
    \text{delete} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma \\
    \text{keep} & \text{otherwise}.
    \end{cases}
\end{equation}
The parameters $\Trefine > \Tdelete$ can be chosen freely.
Chebyshev's inequality
\begin{equation}
  \label{eq:chebychev}
  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2},
\end{equation}
with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.
This inequality holds for arbitrary distributions under the weak assumption that their mean $\mu$ and standard deviation $\sigma$ are finite~\cite{wasserman2004all}.

We use a \muscl{}-hancock based finite volume limiting as proposed in~\cite{dumbser2016simple}.
Briefly, we first compute a candidate solution with our \aderdg{}-scheme and check whether it is valid.
A solution is considered to be invalid if it is a non-finite floating point number or if it is unphysical, i.e.\ if the pressure or density are not positive.
\todo{dmp?}
In case of an invalid solution, we recompute the timestep with a limited \muscl{} finite volume method\todo{Source for the fv method}.

@@

\todo{Constants of fluids?}
A simple scenario is the Taylor-Green vortex.
It has an analytical solution in the incompressible limit which is given by
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) \cos(y) \\
- \cos(x) \sin(y) 
    \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C.
  \end{split}
\end{align}
The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
We use a viscosity of $\mu = 0.1$ and Cauchy boundary conditions.

@@

As a final example of standard flow scenarios, we consider the lid-driven cavity flow which initial conditions are given by a fluid at rest, with $\Qrho = 1, \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.

We consider a domain of size $\SI{2\pi}{m} \times \SI{2\pi}{\m}$ which is surrounded by no-slip walls.
The flow is driven entirely by the upper wall which has a velocity of $v_x = \SI{1}{\m/\s}$.
The simulation runs for $\SI{10}{\s}$

Our atmospheric flow scenarios are described in terms of the potential energy
\begin{equation}
  \potT = T \left( \frac{p_0}{p} \right)^{R/c_p},
\end{equation}
with reference pressure $p_o = \SI{10e5}{\Pa}$~\cite{muller2010adaptive,giraldo2008study}.
For all remaining scenarions, we use the constants
\begin{equation}\label{eq:atmosphere-constants}
    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = 10000, \qquad g = 9.8.
\end{equation}

We compute the initial background density and pressure by inserting the assumption of a constant background energy in \cref{eq:hydrostatic-balance}.
The background atmosphere is then perturbed.
\todo{What about our weird boundary condition for heat flux and energy?}
Let
\begin{equation}
  \label{eq:radius}
  r^2 = (x - x_0)^2 + (z - z_0)^2
\end{equation}
denote the difference between spatial positions $x,z$ and the center of a bubble $x_c, z_c$.
For our first scenario, the cosine bubble, we use a pertubation of the form
\begin{equation}
  \label{eq:cos-pertubation-alt}
  \pertubationPotT = 
    \nicefrac{A}{2} \left( 1 + \cos(\pi r) \right) \left[ r \leq a \right]
\end{equation}
\begin{align}
  \label{eq:cos-pertubation}
  \pertubationPotT &= \begin{cases}
    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a, \\
    0 & r > a,
    \end{cases}
\end{align}
where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
We use the constants
\begin{equation}\label{eq:cosine-bubble}
  A = 0.5 \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
\end{equation}
We use a constant viscosity of $\mu = 0.1$.
For our second scenario, the cold bubble on top of a warm bubble, we use the pertubations
\begin{equation}
  \label{eq:bubbles-pertubation}
  \pertubationPotT =
  \begin{cases}
    A & r \leq a, \\
    A \exp \left( - \frac{(r-a)^2}{s^2} \right) & r > a,
    \end{cases}
\end{equation}
where $s$ is the decay rate and $r$  is the radius to the center~\pcref{eq:radius}.
We have two bubbles, with constants
\begin{equation}
  \label{eq:bubbles-values}
\begin{alignedat}{6}
  & \text{warm:} \qquad && A = 0.5, \quad&& a = \SI{150}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{500}{\m,} \quad&& z_c = \SI{300}{\m},\\
  & \text{cold:} \qquad && A = -0.15, \quad&& a = \SI{0}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{560}{\m}, \quad&& z_c = \SI{640}{\m}.
  \end{alignedat}
\end{equation}
Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.
To ensure that the atmosphere stays in hydrostatic balance~\cite{giraldo2008study}, we need to impose the viscous heat flux\todo{Show full bc?}
\begin{equation}
  \label{eq:atmosphere-bc}
  \viscFlux_{\QE} = \kappa \pdv{\overline{T}}{z}% =
%\kappa \frac{R \overline{\theta} \left(\frac{\overline{p}{\left (z \right )}}{p_{0}}\right)^{\frac{R}{c_{p}}} \frac{d}{d z} \overline{p}{\left (z \right )}}{c_{p} \overline{p}{\left (z \right )}}.
\end{equation}

@@

TODO, Show following results:
\begin{itemize}
\item Simple cfd: Taylor Green, ABC, Lid Driven Cavity
\item Two Bubbles with and without amr
\item Limited Reactive euler/and maybe ns
\end{itemize}

\section{Conclusion}
We presented a \muscl{}-limited \aderdg{}-scheme with \amr{} for the reactive Navier-Stokes equations.
Our implementation is capable of simulating different scenarios:
\begin{itemize}
  % Convergence test?
\item We evaluated our method for standard \textsc{cfd} scenarios and achieved competitive results for all used scenarios.
  This is true for both two-dimensional scenarios (Taylor-Green vortex and lid-driven cavity) and for the three-dimensional \textsc{abc}-flow.
\item Furthermore, our method allows us to simulate flows in hydrostatic equilibrium correctly.
\item We showed that our \amr{}-criterion is able to vastly reduce the number of grid cells while preserving the quality of the results.
\item Our results of for the reactive detonation waves showed that our implementation is capable of simulating chemical reactions with a limited scheme, at least for a non-stiff source term.
\end{itemize}
